# Results

Now that we have the list of city destinations, it would be useful to profile the known population holidaying to these destinations. A useful comparison would be to compare the customer population holidaying to these locations with the Leeds holiday making population as a whole. The figure 3 demonstrates the extent to which the holiday makers to the destinations of interest differ from the Leeds holiday-making population, particularly in terms of 5 demographic variables, age band, household income, number of children, overall satisfaction and supergroup name. From the figure below3, a consumer profile of holidaymakers to American cities starts to emerge. Consumers traveling to these locations are aged between 35 to 49, have a household income of between 41-50 thousand, have children, there seems to be a concentration of consumers with 2 children, were poorly satisfied with their most recent holiday and belong to the Suburbanites super group. From this it can be inferred that the consumers holidaying to these locations are young professionals, living in suburban areas, have a comfortable income, and have at least one child.

```{r, echo=FALSE, fig.width=10, fig.height=10, message=FALSE, warning=FALSE, fig.cap="Difference in Proportion of Characteristics off Holidaymakers to Orlando and Las Vegas"}
#Create a vector of the names of grouping variables that will be summarised over.
groups <- names(simulated_oac_age_sex %>%
                  select(supergroup_name, age_band:household_income, satisfaction_overall))
# Identify the destination in focus.
focus <- c("SFB","LAS", "MCO")
control <- "ALL"

# calculate_props() requires control and focus variables, not yet contained in
# simulated dataset. Create a new dataset with these added.
temp_simulated_data <- simulated_oac_age_sex %>%
  mutate(
    focus_var=if_else(overseas_airport %in% focus,1,0),
    control_var=1,
    focus_total=sum(focus_var),
    control_total=sum(control_var),
    number_children=as.character(number_children)
 )

# Iterate over each grouping variable, using map_df to bind rows of returned
# data frames.
temp_plot_data <-
 purrr::map_df(groups, ~calculate_props(temp_simulated_data, rlang::sym(.x)))
rm(temp_simulated_data)

# Define two colours used to colour pos and neg bars differently
fill_colours <- c("#ffffff", "#cccccc")
plot5 <- temp_plot_data %>%
  gather(key=stat_type, value=stat_value, -c(variable_type, variable_name)) %>%
  mutate(
    stat_type=factor(stat_type, levels=c("focus_prop","control_prop","diff_prop")),
    stat_sign=stat_value>0
  ) %>%
  filter(!is.na(variable_name)) %>%
  ggplot(aes(x=variable_name, y=stat_value))+
  # stat_sign is a boolean identifying whether stat_value is pos or neg.
  geom_col(aes(fill=stat_sign), colour="#636363", size=0.3)+
  scale_fill_manual(values=fill_colours, guide=FALSE)+
  facet_grid(variable_type~stat_type, scales="free", space="free_y")+
  labs(caption=paste0("focus var : SFB, MCO, LAS "," | control var : ",control))+
  coord_flip()+
  theme(axis.title=element_blank(), strip.text.y = element_text(angle=0))+ 
  theme_minimal()+theme(
   strip.text.y = element_text(angle=0))+ylab("")+xlab("")

# Print plot to console
plot5
```

Expanding upon these findings, it is possible to map the geographical distribution of holidaymakers with the distinguishing characteristics, in this case in the age band 35 to 49, have at least one child, are suburbanites, and were poorly satisfied with their most recent holiday. Unsurprisingly given that the holidaymakers traveling to the destinations of interest are distinctively suburbanites, the figure above shows that they are located towards the peripheries of the study area or in areas that can be considered more suburban. In fact, upon closer inspection, it seems that there are no/close to zero holidaymakers in the city centre and its immediate periphery traveling to the locations of
interest.

```{r,echo=FALSE, fig.width=10, fig.height=10, message=FALSE, warning=FALSE, fig.cap="Geographical Distribution of Target Market"}
# Mapp survey variables of choice?
temp_target_data <-
  simulated_oac_age_sex %>%
    summarise(
      oa_code=zone,
      is_target_age=as.numeric(age_band %in% c("a35to49")),
      is_target_children=as.numeric(number_children>0),
      is_target_geodeom=as.numeric(supergroup_name =="Suburbanites"),
      is_target_satisfaction=as.numeric(satisfaction_overall == "1_poor")
) %>% 
  rowwise() %>%
  mutate(
    target_extent=sum(is_target_age,is_target_children, is_target_geodeom)
    ) %>%
  ungroup() %>%
  mutate(
      target_extent_coded=
      case_when(
        target_extent == 4 ~ "high",
        target_extent == 3 ~ "high",
        target_extent == 2 ~ "mid",
        target_extent == 1 ~ "low",
        TRUE ~ ""
        )
  ) %>%
  group_by(oa_code) %>%
  summarise(
    high=sum(as.numeric(target_extent_coded=="high")),
    mid=sum(as.numeric(target_extent_coded=="mid")),
    low=sum(as.numeric(target_extent_coded=="low")),
    index=sum(target_extent)
  )
# Plot high to low chloropeth maps:
plot7 <- oa_boundaries %>%
left_join(temp_target_data  %>%
          pivot_longer(
            cols=c(high),
            names_to="target_extent",
            values_to="count")
        ) %>%
mutate(
  target_extent=
  factor(target_extent, levels=c("high"))
) %>%
ggplot()+
  geom_sf(aes(fill=count), colour=NA)+
  geom_sf(data=. %>% summarise(),
    fill="transparent", colour="#756bb1", size=0.2)+
  coord_sf(crs=st_crs(oa_boundaries), datum=NA)+
  scale_fill_distiller(palette="Purples", direction=1)+theme_minimal()
  # facet_wrap(~target_extent, nrow=3)+theme_minimal()
##
plot7
```

